Spatial Reasoning and Data Displays

### 2015-01-19 Paper/Draft1/TestingVisualAptitude.Rnw
Address "this study"

\comment{`This study' - you still have not established that there is a study. Say it. In this paper we discuss the results of a study .... and now describe what this study tests.}
\newtext{This study is designed to compare lineup performance with visual aptitude and reasoning tests, examining the skills necessary to successfully evaluate lineups. }
We compare lineup performace to the visual search task (VST), paper folding test, card rotation test, and figure classification test. 
The VST measures visual search speed\cite{goldstein1973validity}, the paper folding and card rotation tests measures spatial manipulation ability, and the figure classification test measures inductive reasoning\cite{ekstrom1976manual}; 
all of these skills are at least peripherally recruited during the lineup task, but some may dominate in predicting performance on the lineup task. 
We hope to facilitate comparison of the lineup task to known cognitive tests, inform the design of future studies, and better understand the perception of statistical lineups.

>>>>

% \comment{`This study' - you still have not established that there is a study. Say it. In this paper we discuss the results of a study .... and now describe what this study tests.}
\newtext{In this paper, we present the results of a study designed to compare lineup performance with visual aptitude and reasoning tests, examining the skills necessary to successfully evaluate lineups. }
We compare lineup performace to the visual search task (VST), paper folding test, card rotation test, and figure classification test. 
The VST measures visual search speed\cite{goldstein1973validity}, the paper folding and card rotation tests measures spatial manipulation ability, and the figure classification test measures inductive reasoning\cite{ekstrom1976manual}; 
all of these skills are at least peripherally recruited during the lineup task, but some may dominate in predicting performance on the lineup task. 
We hope to facilitate comparison of the lineup task to known cognitive tests, inform the design of future studies, and better understand the perception of statistical lineups.
